---
title: "Lab 00 - Hello IDS!"
author: "STEPAN MIKOYAN"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Stepan Mikoyan", "Mason Moir", 
           "Lucas Salhani", "Blair Rafferty"),
  github_username = c("mcgregors-garden", "stepstolgory", "masonmoir", 
                      "lsalhani", "B-Rafferty"), 
  colour = c("powderblue", "mediumorchid3", "deepskyblue1", 
             "grey2", "gray29"),
  hobby = c("Hopping", "Climbing", "Rugby", 
            "Swimming", "Rugby"),
  favourite_number = c(2, 7, 8, 1, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Bar plot showing the github usernames as well as the user's favourite colour and number

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "Favourite number",
          title = "Bar plot about group members")
```

labs() adds the labels to the bar plot

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```
If this plot was used for the whole course, it's likely that it will be lost of very small values. Perhaps grouping the hobbies into broader categories such as "sports", "arts", etc and then using a stacked bar chart will provide a nicer representation.

