---
title: "Lab 00 - Hello IDS!"
author: "STEPAN MIKOYAN"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Stepan Mikoyan", "Mason Moir", 
           "Lucas Salhani", "Blair Rafferty"),
  github_username = c("mcgregors-garden", "stepstolgory", "masonmoir", 
                      "lsalhani", "B-Rafferty"), 
  colour = c("powderblue", "mediumorchid3", "deepskyblue1", 
             "grey2", "gray29"),
  hobby = c("Hopping", "Climbing", "Rugby", 
            "Swimming", "Rugby"),
  favourite_number = c(2, 7, 8, 1, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Bar plot showing the github usernames as well as the users favourite colour and number

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
